Correlation between different emission channels from an atom inside a leaky driven cavity

### 2019-12-09 newpaper.tex
Add files via upload

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.7]{lastgraph.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500. (a) We consider $\kappa = $0.1 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.

@@

%In Fig. \ref{errorzz} we can appreciate that, as we increase the total temporal interval, the cavity linewidth at which the correlation starts decreasing is smaller. This supports the idea that the time that takes for the system in stablishing the number photons will affect the minimum value of cavity linewidth at which the correlation starts decreasing.

>>>>

\begin{center}
\begin{figure*}[!t]
\begin{center}
\includegraphics[scale = 0.7]{lastgraph1.pdf}
\caption{\small{Mean value of spontaneous emissions after post-selection, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$ and with tf = 500. (a) We consider $\kappa = $0.05 which has a correlation value around $0.1$; (b) we consider $\kappa = $1.0, which has a correlation value around $0.01$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
The results are shown in Fig. \ref{corrxy}. We see a maximum
correlation close to $0.1$ for $\kappa/\gamma\approx 0.05$ that
decreases as $\kappa$ increases. From the figure it looks like the
correlation goes to zero as $\kappa\rightarrow\infty$. With values for
$\kappa/\gamma$ lower than $0.05$, we notice that the correlations
increase stops and a decrease begins. This stop in the increase of the
correlation is due to the fact that, as we keep decreasing the cavity
linewidth the number of photons that leaks the cavity decreases
considerably. In the limit where $\kappa=0$ the two random
variables becomes independent, because the output of $n_c$ is zero
with probability one. In this case there is no correlation between the two
random variables.

@@

%In Fig. \ref{errorzz} we can appreciate that, as we increase the total temporal interval, the cavity linewidth at which the correlation starts decreasing is smaller. This supports the idea that the time that takes for the system in stablishing the number photons will affect the minimum value of cavity linewidth at which the correlation starts decreasing.
Studying this correlation further, we see how the average number of
spontaneous emissions varies given the number of cavity emissions during a constant length of time. Making a 
post-selection around the average number of cavity emissions we make a gaussian
adjustment for the average number of spontaneous emissions and the corresponding 
standard deviation. Such results are shown in Fig. \ref{probdisult}, where we notice that
for the case in which we have a correlation around $0.1$, making a post-selection with a 
bigger number of cavity emissions turns into an increase of the mean number of spontaneous emissions,
 while the opposite happens for a lower number of cavity emissions. On the other hand, when 
the correlation is around $0.01$, the change in the average number of spontaneous emissions
after the post-selection is barely noticeable.
